math.md
Analysis of Audio Link Pattern Validity
The provided audio link pattern for Geometry Dash song downloads is expressed as follows:
Link: https://audio−download.ngfiles.com/(ID−Mod(ID,1000)ID)/(ID)(Modified name with limit of 26 characters).mp3 \text{Link: } https://audio-download.ngfiles.com/(ID - \frac{{\text{Mod}(ID, 1000)}}{{ID}})/(ID)_(\text{Modified name with limit of 26 characters}).mp3 Link: https://audio−download.ngfiles.com/(ID−IDMod(ID,1000)​)/(ID)(​Modified name with limit of 26 characters).mp3This pattern is contingent upon an intrinsic mathematical property, specifically the Modulo operation, denoted as Mod(a,b)\text{Mod}(a, b)Mod(a,b), which yields the remainder when aaa is divided by bbb. The efficacy of the provided link is subject to the condition that the ID (IDIDID) exceeds or is equal to 469775.
Explanation:
Let k k k represent the ID (IDIDID), and let Mod(k,1000) \text{Mod}(k, 1000) Mod(k,1000) be the result of the modulo operation with 1000 as the divisor. The pattern relies on the fact that the quotient Mod(k,1000)k \frac{{\text{Mod}(k, 1000)}}{{k}} kMod(k,1000)​ is utilized as a subtractive factor in the construction of the audio link.
Mathematical Justification:
The crux of the matter lies in the behavior of Mod(k,1000)k \frac{{\text{Mod}(k, 1000)}}{{k}} kMod(k,1000)​ as k k k varies. Consider the limit as k k k approaches positive infinity:
lim⁡k→∞Mod(k,1000)k \lim_{{k \to \infty}} \frac{{\text{Mod}(k, 1000)}}{{k}} k→∞lim​kMod(k,1000)​As k k k tends towards infinity, the numerator (Mod(k,1000) \text{Mod}(k, 1000) Mod(k,1000)) remains bounded by 1000. Consequently, the fraction Mod(k,1000)k \frac{{\text{Mod}(k, 1000)}}{{k}} kMod(k,1000)​ tends towards zero. Therefore, for sufficiently large values of k k k, the subtractive term Mod(k,1000)k \frac{{\text{Mod}(k, 1000)}}{{k}} kMod(k,1000)​ becomes negligible.
Implication:
For values of k k k prior to 469775, the subtractive factor dominates the link construction, resulting in a negative or fractional component that disrupts the integrity of the link. Hence, the provided pattern is valid only for k≥469775 k \geq 469775 k≥469775, ensuring that the subtractive factor is inconsequential in relation to the overall link construction.
In summary, the restriction to k≥469775 k \geq 469775 k≥469775 is a safeguard against mathematical aberrations, ensuring the reliability of the Geometry Dash song download link pattern.